\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-19 doc/flexiblesusy-paper.tex
changed sentence just before Design Goal to reinstate original meaning - we pass the outut *to* other codes both private and public.

The standard input and output of the generated spectrum generator is
the SLHA format \cite{Skands:2003cj,Allanach:2008qq}, which is
intended for the communication between MSSM and NMSSM spectrum
generators and observable calculators.  The user has control over the
SLHA block names by editing the SARAH model files and may also add
extra blocks in the \code{FlexibleSUSY.m} model file, as described in
\secref{sec:modfile}.
%
% We use SLHAea \cite{slhaea} to create these SLHA files and with
% simple modifications these can be passed directly to another code
% which uses them as an alternative to writing out the SLHA file.
%
We have tested that the HDECAY $3.4$ \cite{hdecay} and SDECAY $1.4$
\cite{sdecay}, which are shipped with SUSY-HIT \cite{susyhit},
understand the SLHA output of \fs and give matching output to that
from Softsusy.
%
For models which go beyond the MSSM and NMSSM no fixed standard exists
which specifies the spectrum generator input and output format.  For
this reason, \fs allows the user to control the SLHA input and output
blocks in order to simplify the process of passing the output of a
custom \fs-generated spectrum generator or any new public tool
developed for that model.

>>>>

The standard input and output of the generated spectrum generator is
the SLHA format \cite{Skands:2003cj,Allanach:2008qq}, which is
intended for the communication between MSSM and NMSSM spectrum
generators and observable calculators.  The user has control over the
SLHA block names by editing the SARAH model files and may also add
extra blocks in the \code{FlexibleSUSY.m} model file, as described in
\secref{sec:modfile}.
%
% We use SLHAea \cite{slhaea} to create these SLHA files and with
% simple modifications these can be passed directly to another code
% which uses them as an alternative to writing out the SLHA file.
%
We have tested that the HDECAY $3.4$ \cite{hdecay} and SDECAY $1.4$
\cite{sdecay}, which are shipped with SUSY-HIT \cite{susyhit},
understand the SLHA output of \fs and give matching output to that
from Softsusy.
%
For models which go beyond the MSSM and NMSSM no fixed standard exists
which specifies the spectrum generator input and output format.  For
this reason, \fs allows the user to control the SLHA input and output
blocks in order to simplify the process of passing the output of a
custom \fs-generated spectrum generator to any private or new public
tool developed for that model.
